Spin canonical divisors of log stacky curves

### 2015-06-26 stacky_write_up/spin_cring.tex
rephrased lemma 3.3

\begin{lem}\label{lem:relations_from_generators_induction} 
Suppose $\halfcan$ and $\halfcan'$ are $\BQ$ divisors on a curve $X$ with $D=D'+\frac{\alpha}{\beta}P$.  Suppose $R_{\halfcan'}$ is generated by $x_1, \ldots, x_m$ and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over $R_{\halfcan'}$; specifically, suppose there is a $k$-basis $S$ for $R_\halfcan$ over $R_{\halfcan'}$ such that $S$ consists only of monomials in $x_1, \ldots, x_m, y_1, \ldots, y_n$ and each $m\in S$ is not contained in $R_{\halfcan'}$.  
Let $I$ and $I'$ be the ideals of relations of $R_{\halfcan'}$ and $R_{\halfcan}$, for the given generating sets.  
Let $T\subseteq R_\halfcan - (S \cup R_{\halfcan'})$, such that any monomial of $(k[x_1, \ldots, x_m, y_1, \ldots, y_n])_{\ge 2}$ (the degrees at least 2 with respect to the regrading of each $x_1, \ldots, x_m, y_1, \ldots, y_n$) is either in $S$, $\langle T\rangle$, or $I' k[x_1, \ldots, x_m, y_1, \ldots, y_n]$.  Moreover, suppose there is some ordering $\prec$ such that if $T\prec S\prec k[x_1, \ldots, x_n]$ (that is, all elements of $T$ precede elements of $S$ which proceed monomials only in the $x_i$s). , then 
\begin{align*}
	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
		     & + \langle T \rangle.
\end{align*}
\end{lem}
\begin{proof}
Suppose monomial $f\in T$ has a pole order $a$ at $P$.  Then since $S$ forms a $k$-basis of $R_{\halfcan}$ over $R_{\halfcan'}$, we can write $f + (\sum_{g\in S'} C_g g)+r$ for some finite subset $S'\subseteq S_{\deg(f)}$ and $r\in R_{\halfcan'}$.  This demonstrates that 
\begin{align*}
	\initial(I) & \supseteq \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
		     & + \langle T \rangle.
\end{align*}
Since every monomial of $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ either lies in $\langle T\rangle + \initial_\prec(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ or $S$, 
\begin{align*}
	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
		     & + \langle T \rangle.
\end{align*}
\end{proof}

>>>>

\begin{lem}\label{lem:relations_from_generators_induction} 
Suppose $\halfcan$ and $\halfcan'$ are $\BQ$ divisors on a curve $X$ with $\halfcan=\halfcan'+\frac{\alpha}{\beta}P$, that $R_{\halfcan'}$ is generated by $x_1, \ldots, x_m$ and $R_{\halfcan}$ is minimally generated by $y_1, \ldots, y_n$ over $R_{\halfcan'}$ with ideals of relations $I'$ and $I$ respectively.  Suppose there are sets of monomials $S\subseteq R_\halfcan-R_{\halfcan'}$ and $T\subseteq R_\halfcan-(S\cup R_\halfcan')$, and an ordering $\prec$ such 
\begin{enumerate}
\item $T\prec S\prec k[x_1, \ldots, x_n]$ (meaning all monomials in $T$ precede all monomials in $S$ which proceed all monomials in $k[x_1, \ldots, x_n]$)
\item $S$ forms a $k$-basis for $R_\halfcan$ over $R_\halfcan'$
\item All monomials in $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ lie in 
\begin{align*}
	& S \\
	\cup \; &\langle T\rangle \\
	\cup \; & \initial_\prec{I'} k[x_1, \ldots, x_m, y_1, \ldots, y_n]
\end{align*}
\end{enumerate}
Then 
\begin{align*}
	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
		     & + \langle T \rangle.
\end{align*}
\end{lem}
\begin{proof}
Suppose monomial $f\in T$ has a pole order $a$ at $P$.  Then since $S$ forms a $k$-basis of $R_{\halfcan}$ over $R_{\halfcan'}$, we can write $f + (\sum_{g\in S'} C_g g)+r$ for some finite subset $S'\subseteq S_{\deg(f)}$ and $r\in R_{\halfcan'}$.  This demonstrates that 
\begin{align*}
	\initial(I) & \supseteq \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
		     & + \langle T \rangle.
\end{align*}
Since every monomial of $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ either lies in $\langle T\rangle + \initial_\prec(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ or $S$, 
\begin{align*}
	\initial(I) & = \initial(I') k[x_1, \ldots, x_m, y_1, \ldots, y_n]\\
		     & + \langle T \rangle.
\end{align*}
\end{proof}
